---
title: "My Fancy Presentation"
author: "MvL"
date: "1 november 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
Some content

***
A slide without a title

## My title
### A top level subheading
#### A second subheading

- Bullet one
- Bullet two

1. Item a
2. Item b

## Formatting options

Plain text

*italicized text*

**Bold text**

`for (i %in% 1 : 10)`

## R code


```{r head, echo = TRUE, comment= ""}
head(mtcars)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, echo= FALSE, fig.align='center', fig.cap='My awesome plot', fig.height=6}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

